Honey Bees - edgeR

### 2018-04-11 N_V/EdgeR/edgeR-btwnLane/makeDataMetrics.Rmd
Standard scatterplots Gailbraith data

---
title: "Honey Bees - edgeR"
author: Lindsay Rutter
output:
  packagedocs::package_docs:
    toc: true
    toc_collapse: true
vignette: >
  %\VignetteEngine{packagedocs::redirect}
---

@@

```{r}
minLib <- min(y$samples$lib.size)
keep <- rowSums(cpm(y)>4) >= 6
# Number of genes 15,314--> 8,672
y <- y[keep, , keep.lib.sizes=FALSE]
```

>>>>

---
title: "Honey Bees - edgeR-btwnLane"
author: Lindsay Rutter
output:
  packagedocs::package_docs:
    toc: true
    toc_collapse: true
vignette: >
  %\VignetteEngine{packagedocs::redirect}
---

@@

```{r}
minLib <- min(y$samples$lib.size)
nRep = length(lapply(colnames(beeCounts), function (x) unlist(strsplit(x, "[.]"))[1])) / length(unique(lapply(colnames(beeCounts), function (x) unlist(strsplit(x, "[.]"))[1])))
keep <- rowSums(cpm(y)>round(minLib/1000000)) >= nRep/2
# Number of genes 15,314--> 8,672
y <- y[keep, , keep.lib.sizes=FALSE]
```

### 2018-04-11 N_V/EdgeR/edgeR/makeDataMetrics.Rmd
Completed DEG for all platforms for N_V
Standard scatterplots Gailbraith data

```{r}
minLib <- min(y$samples$lib.size)
keep <- rowSums(cpm(y)>4) >= 6
# Number of genes 15,314--> 8,672
y <- y[keep, , keep.lib.sizes=FALSE]
```

Next, I used edgeR normalization.
```{r}
y[[1]] <- betweenLaneNormalization(y[[1]], which="full", round=FALSE)
```

>>>>

```{r}
minLib <- min(y$samples$lib.size)
nRep = length(lapply(colnames(beeCounts), function (x) unlist(strsplit(x, "[.]"))[1])) / length(unique(lapply(colnames(beeCounts), function (x) unlist(strsplit(x, "[.]"))[1])))
keep <- rowSums(cpm(y)>round(minLib/1000000)) >= nRep/2
# Number of genes 15,314--> 8,672
y <- y[keep, , keep.lib.sizes=FALSE]
```

Next, I used edgeR normalization.
```{r}
y <- calcNormFactors(y)
```

### 2018-04-11 VirusHoneyBee/EdgeR/edgeR/makeDataMetrics.Rmd
Standard scatterplots Gailbraith data

```{r}
minLib <- min(y$samples$lib.size)
keep <- rowSums(cpm(y)>6) >= 3
# Number of genes 15,314--> 8,672
y <- y[keep, , keep.lib.sizes=FALSE]
```

>>>>

```{r}
minLib <- min(y$samples$lib.size)
nRep = length(lapply(colnames(beeCounts), function (x) unlist(strsplit(x, "[.]"))[1])) / length(unique(lapply(colnames(beeCounts), function (x) unlist(strsplit(x, "[.]"))[1])))
keep <- rowSums(cpm(y)>round(minLib/1000000)) >= nRep/2
# Number of genes 15,314--> 8,672
y <- y[keep, , keep.lib.sizes=FALSE]
```
